---
title: "dev_history.Rmd for working package"
author: "Sébastien Rochette"
date: "23/01/2021"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r development, include=FALSE}
library(testthat)
library(dplyr)
```

<!--
# Description of your package

This will fill the description of your package.
Add this chunk using `fusen::description_chunk()`
--> 

```{r description}
# Describe your package
fusen::fill_description(
  fields = list(
    Title = "Exploratory of NYC Squirrel Census",
    Description = "Example of the use of {fusen} with Rmd First method to build a package.",
    `Authors@R` = c(
      person("Sebastien", "Rochette", email = "sebastien@thinkr.fr", role = c("aut", "cre"), comment = c(ORCID = "0000-0002-1565-9313")),
      person(given = "ThinkR", role = "cph")
    )
  )
)
# Define License with use_*_license()
usethis::use_mit_license("Sébastien Rochette")
```

# Read data

<!-- Store your dataset in a directory named "inst/" at the root of your project -->
<!-- Use it for your tests in this Rmd thanks to `load_all()` to make it available
and `system.file()` to read it in your examples 
-->

```{r development-2}
# Run all in the console directly
# Create "inst/" directory
dir.create(here::here("inst"))
# Example dataset
file.copy(system.file("nyc_squirrels_sample.csv", package = "fusen"), here::here("inst"))
# Make your dataset file available to the current Rmd
pkgload::load_all(path = here::here(), export_all = FALSE)
# You will be able to read your example data file in each of your function examples and tests as follows
# datafile <- system.file("nyc_squirrels_sample.csv", package = "fusen.squirrels")
# nyc_squirrels <- read.csv(datafile)
```

# Check the validity of the entry dataset

```{r function-1}
#' Check data integrity
#'
#' @param x dataframe with at least colums lat, long and primary_fur_color
#'
#' @return Original dataframe if all tests are good. Otherwise stops.
#' @export
#'
#' @examples
check_data_integrity <- function(x) {
  # Verify it is a data.frame
  if (!is.data.frame(x)) {stop("x is not a dataframe")}
  
  # Verify points are in New York around Central Park
  all_coords_ok <- all(
    c(min(x[["lat"]]) > 40.76400,
      max(x[["lat"]]) < 40.80100,
      min(x[["long"]]) > -73.98300,
      max(x[["long"]]) < -73.94735)
  )
  if (!all_coords_ok) {stop("Not all data are in Central Park")}
  
  # Verify there is only one color in primary_fur_color.
  # A `+` is a sign of multiple colours
  if (any(grepl("+", x[["primary_fur_color"]], fixed = TRUE))) {
    stop("There are multiple colors in some 'primary_fur_color'")
  }
  
  message("All tests are good !")
  return(x)
}

```

```{r example-1}
datafile <- system.file("nyc_squirrels_sample.csv", package = "fusen.squirrels")
nyc_squirrels <- read.csv(datafile)
nyc_squirrels_ok <- check_data_integrity(nyc_squirrels)
```

```{r test-1}
datafile <- system.file("nyc_squirrels_sample.csv", package = "fusen.squirrels")
nyc_squirrels <- read.csv(datafile)
nyc_squirrels_ok <- check_data_integrity(nyc_squirrels)

test_that("check_data_integrity works correctly", {
  # Ok
  expect_message(check_data_integrity(nyc_squirrels), "All tests are good !")
  
  # No dataframe
  expect_error(check_data_integrity("vector data"), "x is not a dataframe")
  
  # False latitude
  old_ok <- nyc_squirrels[["lat"]][1]
  nyc_squirrels[["lat"]][1] <- 12
  expect_error(check_data_integrity(nyc_squirrels), "Not all data are in Central Park")
  nyc_squirrels[["lat"]][1] <- old_ok
  
  # Error primary_fur_color
  old_ok <- nyc_squirrels[["primary_fur_color"]][1]
  nyc_squirrels[["primary_fur_color"]][1] <- "grey+pink"
  expect_error(check_data_integrity(nyc_squirrels), "There are multiple colors in some 'primary_fur_color'")
  nyc_squirrels[["primary_fur_color"]][1] <- old_ok
})
```

# Inflate your package

You're one inflate from paper to box.
Build your package from this very Rmarkdown using `fusen::inflate()`

```{r development-4, eval=FALSE}
fusen::inflate(rmd = here::here("dev/dev_history.Rmd"))
```

- Verify your `"DESCRIPTION"` file has been updated
- Verify your function is in `"R/"` directory
- Verify your test is in `"tests/testthat/"` directory
- Verify this Rmd appears in `"vignettes/"` directory

# Present and admire the content of your package
## Presentation with a README

```{r development-3, eval=FALSE}
devtools::install()
usethis::use_readme_rmd()
```

## Presentation with the associated website

```{r development-4, eval=FALSE}
# page for coverage
remotes::install_github('yonicd/covrpage')
covrpage::covrpage(vignette = TRUE)
# pkgdown website
pkgdown::build_site()
usethis::use_build_ignore("docs/") # Hide from package build
usethis::use_git_ignore("docs/") # Do not send on Git
# Check everything is good
rcmdcheck::rcmdcheck()
# Add checks on GitHub Actions and pkgdown
usethis::use_github_action_check_standard() # Check using CI
usethis::use_github_action("pkgdown") # Allow for pkgdown
```


